Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-21 Submission.Rmd
bartletts test and histograms

>>>>

## Standard deviations of perceptions

```{r overallhist, fig.cap="Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands."}

## resource$sd

toplotresource <- resource
toplotchallenge <- challenge
toplothindrance <- hindrance

toplotresource$RD <- "Resource"
toplotchallenge$RD <- "Challenge"
toplothindrance$RD <- "Hindrance"

toplottogether <- rbind(toplotresource,toplotchallenge,toplothindrance)

library(ggplot2)
#ggplot(resource, aes(x=sd)) + geom_histogram()
ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .)

lookie <- stats::bartlett.test(sd ~ RD, toplottogether)

Figure \@ref(fig:overallhist) presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $K^2$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).

### 2022-12-21 Submission.tex
bartletts test and histograms

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  \emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
\item
  \emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
\item
  \emph{Research Question 3}: Are literature-implicated hidrances consistently rated as job hindrances?
\end{enumerate}

@@

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  \emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
\item
  \emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
\item
  \emph{Research Question 3}: Are literature-implicated hindrances consistently rated as job hindrances?
\end{enumerate}

@@

\hypertarget{standard-deviations-of-perceptions}{%
\subsection{Standard deviations of perceptions}\label{standard-deviations-of-perceptions}}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
\caption{\label{fig:overallhist}Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands.}
\end{figure}

Figure \ref{fig:overallhist} presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).
